### 2013-03-28 doc/sosp13/evaluation.tex
data in table form

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{results/benchmarks.pdf}
    \end{center}
    \caption{Comparing \Grappa with XMT, hand-tuned MPI and UPC.}
    \label{fig:grappa-comparisons}
\end{figure}

Figure~\ref{fig:grappa-comparisons} shows the results. Overall, \Grappa is
within striking distance of XMT and UPC performance. However, it underperforms
compared to hand-tuned MPI. Nevertheless, this comparison needs to be taken
with a grain of salt for several reasons. First, we have not spent as much
time tuning \Grappa's implementations. This is supported by inspecting the BFS
MPI implementation we used, which clearly shows that it employs a lot of
algorithmic-specific optimizations. In fact, some of these optimizations
resemble some of what \Grappa does automatically, like message aggregation.
Second, the GUPS results presented earlier suggests that \Grappa performance
can do a lot better. \TODO{update this once we have more results. }

>>>>

% \begin{figure}[ht]
%     \begin{center}
%       \includegraphics[width=0.5\textwidth]{results/benchmarks.pdf}
%     \end{center}
%     \caption{Comparing \Grappa with XMT, hand-tuned MPI and UPC.}
%     \label{fig:grappa-comparisons}
% \end{figure}

\begin{table}[htb]
\begin{center}
\begin{tabular}{l|c|c|c|c}
&	Cora &      XMT	&        MPI	&   UPC \\ \hline
GUPS	& 1	& 2.23	& 0.11& 	-- \\ 
BFS	& 1 &	4.33	& 14.37 & 	-- \\ 
Intsort	& 1	& 3.77 &	5.88	& -- \\
UTS (T1)	& 1	& 0.38	& -- &	0.09 \\ 
Pagerank	& 1	& 4.35	& 4.87 &	-- \\ 
\end{tabular}
\end{center}
\caption{Comparing \Grappa with XMT, hand-tuned MPI and UPC. Numbers are presented as throughput normalized to \Grappa.}
\label{tab:grappa-comparisons}
\end{table}

Table~\ref{tab:grappa-comparisons} shows the results. Overall, \Grappa is
within striking distance of XMT and well beyond UPC performance (UTS only).
However, it underperforms compared to hand-tuned MPI. Nevertheless, this
comparison needs to be taken with a grain of salt for several reasons. First,
we have not spent as much time tuning \Grappa's implementations. This is
supported by inspecting the BFS MPI implementation we used, which clearly
shows that it employs a lot of algorithmic-specific optimizations. In fact,
some of these optimizations resemble some of what \Grappa does automatically,
like message aggregation. Second, the GUPS results presented earlier suggests
that \Grappa performance can do a lot better.
